---
title: "Assignment 7"
Author: "Samriddh Gupta"
output:
  pdf_document: default
  html_notebook: default
  word_document: default
---

## Libraries
```{r}
library(tidyverse)
library(XLConnect)
library(openxlsx)
library(countrycode)
library(purrr)
library(dplyr)
library(ggplot2)
library(gganimate)
theme_set(theme_bw())
library(modelr)
library(broom)
```


## Part 1: Creating our own gapminder animation
All the important URLS
```{r}
if(!file.exists("./data")) {dir.create("./data")}


fileUrls <- c(
  "https://docs.google.com/spreadsheet/pub?key=0AkBd6lyS3EmpdHo5S0J6ekhVOF9QaVhod05QSGV4T3c&output=xlsx",
  "https://docs.google.com/spreadsheet/pub?key=phAwcNAVuyj2tPLxKvvnNPA&output=xlsx",
  "https://docs.google.com/spreadsheet/pub?key=tSUr_yZVbM6a3AGJEq_Z2Pw&output=xlsx",
  "https://docs.google.com/spreadsheet/pub?key=0ArfEDsV3bBwCdHBzUVVSMDlTX1ZCUnNJQ3ZFdkFXVFE&output=xlsx",
  "https://docs.google.com/spreadsheet/pub?key=phAwcNAVuyj0XOoBL_n5tAQ&output=xlsx")

var_names <- c("GDP","life_expectancy", "alt_GDP", "blood press", "population")

```

get_clean function
```{r}

round_df <- function(x, digits) {
    # round all numeric variables
    # x: data frame 
    # digits: number of digits to round
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

get_clean <- function(url_in, var_name){
  tmp = tempfile(fileext = ".xlsx")
  download.file(url_in, destfile = tmp, mode="wb")
  data<-readWorkbook(tmp)
  
  data1<-data %>% 
    rename(country=colnames(data[1])) %>% 
    pivot_longer(-country,names_to = "year",values_to = var_name) %>% 
    na.omit()
  
  data2<-round_df(data1,0)
  data2$year<-as.numeric(data2$year)
  return(data2)
}

setwd("data/")
out1 <- get_clean(fileUrls[1],var_names[1])
head(out1)




```

```{r}
all_data<-map2(fileUrls,var_names,get_clean)
head(all_data)

```

2.	 Join the outputs into one tibble with a column for each variable (hint – perhaps use one of your purrr functions)

```{r}
dat1<-all_data[[1]]
dat2<-all_data[[2]]
dat3<-all_data[[3]]
dat4<-all_data[[4]]
dat5<-all_data[[5]]

dat6<-full_join(dat2,dat1)
dat7<-full_join(dat3,dat4)
dat8<-full_join(dat6,dat7)
join_data<-full_join(dat8,dat5)
join_data
```


```{r}
new_gapminder<-join_data %>% 
  mutate(continent=countrycode(sourcevar = country,
                            origin = "country.name",
                            destination = "continent"))


```


```{r}
new_gapminder<-new_gapminder %>% 
  mutate(continent=case_when(country=="South Yemen (former)"~"Asia",
                             country=="Akrotiri and Dhekelia"~"Europe",
                             country=="Central African Rep."~"Africa",
                             country=="Channel Islands"~"Europe",
                             country=="Cocos Island"~"Asia",
                             country=="Czechoslovakia"~"Europe",
                             country=="East Germany"~"Europe",
                             country=="Eritrea and Ethiopia"~"Africa",
                             country=="Kosovo"~"Europe",
                             country=="North Yemen (former)"~"Asia",
                             country=="North Yemen (former)"~"Americas",
                             country=="St. Martin"~"Asia",
                             country=="Yugoslavia"~"Europe",
                             country=="Serbia and Montenegro"~"Asia",
                             TRUE~continent))

```

```{r}
new_gapminder %>%
  arrange(country, year)

```

## Just for my practice
```{r}
p<-new_gapminder %>% 
  filter(year=="2002") %>% 
  arrange(desc(population)) %>% 
  ggplot(aes(x=GDP,y=life_expectancy))+
  geom_point(aes(size=population,fill=continent),shape=21)+
  scale_x_log10(breaks = 2^(-1:7)*1000)+
  scale_size(range = c(1,20),guide=F)+
  labs(
    x="Income (GDP / capita)",
    y="Life Expectancy (years)"
  )+
  theme_bw()
p
```

## animation

```{r}
plot_data<-new_gapminder %>% 
  select(country,continent,year,GDP,life_expectancy,population) %>% 
  drop_na()


p <- ggplot(
  plot_data, 
  aes(x = GDP, y=life_expectancy)) +
  geom_point(aes(size = population, fill = continent),shape=21)+
  labs(
    x="Income (GDP / capita",
    y="Life Expectancy (years)"
  )+
  theme_bw()+
  scale_x_log10(breaks = 2^(-1:7)*1000)+
  scale_size(range = c(1,20),guide=F)

#p + transition_time(year) +
#  labs(title = "Year: {frame_time}")

p<-p+transition_states(year,transition_length = 1,state_length = 1)+
  ggtitle("year Showing {closest_state}",subtitle = "Frame {frame} of {nframes}")

p

  
```


## Part 2: Analyze life expectancy as function of GDP 

1.	Now, model life expectancy for each country as a function of GDP? (hint – use plot_data from your plot above) 
```{r}

plot_data %>%
  ggplot(aes(GDP, life_expectancy, group = country)) +
  geom_line(alpha = 1/3)+
  scale_x_log10(breaks = 2^(-1:7)*1000)


by_country <- plot_data %>%
  group_by(country, continent) %>%
  nest()

by_country

```


```{r}
country_mod <- function(df){
  lm(life_expectancy ~ GDP, data = df)
}

by_country <- by_country %>%
  mutate(model = map(data, country_mod))
by_country
```

2.	Graph your residuals by country and facet by continent. 
```{r}
by_country <- by_country %>%
  mutate(resids = map2(data, model, add_residuals))
by_country

resids <- unnest(by_country, resids)
resids
```

```{r}
resids %>%
  ggplot(aes(GDP,resid)) +
  geom_line(aes(group = country, color = continent), alpha = 1/3) +
  scale_x_log10(breaks = 2^(-1:7)*1000)+
  geom_smooth(se = FALSE)
```

```{r}
resids %>%
  ggplot(aes(GDP, resid, group = country)) +
  geom_line(alpha = 1/3) +
  scale_x_log10(breaks = 2^(-1:7)*1000)+
  facet_wrap(~continent)
```

3.	Are there countries and continents for which this is a particularly bad model? Use broom::glance to make this determination and provide an explanation for your conclusions. 
```{r}
glance <- by_country %>%
  mutate(glance = map(model, glance)) %>%
  unnest(glance, .drop = TRUE)
glance
```

```{r}

glance %>%
  arrange(r.squared)
```
```{r}
bad_fit <- filter(glance, r.squared < 0.2)
new_gapminder %>%
  semi_join(bad_fit, by = "country") %>%
  ggplot(aes(GDP, life_expectancy, colour = country)) +
  scale_x_log10(breaks = 2^(-1:7)*1000)+
  geom_line()
```
# these are bad fits as there rsquare value is less than 0.2 which means there is less corelation between the life Expectency and GDP.


## Part 3:  
a.	Transform year so that it has a mean of 0
```{r}
transform_data<-plot_data

transform_data$scale_year<-scale(transform_data$year)
mean(transform_data$scale_year)

```
##close to zero

b.	Model with a quadratic polynomial. How can you interpret the coefficients of the quadratic for Belgium? 
```{r}
country_mod1 <- function(df){
  lm(life_expectancy ~ year+scale_year+population, data = df)
}

by_country <- transform_data %>%
  group_by(country, continent) %>%
  nest()

by_country <- by_country %>%
  mutate(model = map(data, country_mod1))

Belgium<-by_country %>% 
  filter(country=="Belgium")

Belgium$model
```
the coeffxicients here tells yes about how each variable effect the life_expectancy and from what we can see here, scale_year does not effect the life_expectancy and other have less relation as well.

c.	Use glance() to identify all countries that do not fit the model well and plot the residuals for the countries that do not fit the model well. 
```{r}
by_country <- by_country %>%
  mutate(resids = map2(data, model, add_residuals))
by_country

resids <- unnest(by_country, resids)
resids

resids %>%
  ggplot(aes(year,resid)) +
  geom_line(aes(group = country, color = continent), alpha = 1/3) +
  geom_smooth(se = FALSE)

#glance1 <- by_country %>%
#  mutate(glance = map(model, glance)) %>%
#  unnest(glance, .drop = TRUE)


```